---
title: "Chapter 3 Exercises: Hacker Edition"
author: "Jenine Harris"
date: "8/22/2020"
output: html_document
---

NOTE: You may want to copy/paste the questions below into your previous week's exercises file.

```{r}
# import data and data management from prior exercises
```



Exercises:

7) Develop a well-formatted table of results including all variables in the small data set (from the previous exercises).

```{r}
# create a table 

```

8) Add a prolog and comments to your code (move this to the top of the file)

```{r}
###########################################
# Project: Chapter 2-3 Coder Exercises
# Purpose: Practice Chapter 2-3 Skills
# Author: Jenine 
# Edit date: September 5, 2020
# Data: 
###########################################

```


9) Summarize the characteristics of transgender survey participants in the 2014 BRFSS.


CHAPTER 3 CODER EXERCISES

Create well-formatted, appropriate graphs for each of the variables below.

1) Income 

```{r}
# Import the data 

# Clean the income, marital status, and race variables 

# Create a graph for income 
```


2) Marital status 

```{r}
# Create a graph of marital status
```


3) Race

```{r}
# Create a graph of race 
```







